Followers Are Not Enough: Beyond Structural Communities in Online Social Networks

### 2014-04-30 paper-for_arxiv/results.tex
Added more discussion to the edge-type work.

Each community type (Structural, Activity-based, Topic-based, Interaction-based) induces a different partition of the edges, and each edge type (Transfer Entropy, Hashtag, Mention-Retweet) induces a different distribution of weights. That is, let $W_{u \to f}$ be the weight on a randomly selected edge $E_{u \to f}$ from the network, and compute
\begin{align}
	P(W_{u \to f} \leq w | T(E_{u \to f}) = t)
\end{align}
where $t$ is one of inter, intra, and multi. For meaningful community structure, we expect the distribution of edge weights to differ depending on the edge type.
These distributions are shown in Figure~\ref{Fig-distributions_by_types}.

Each \emph{column} of Figure~\ref{Fig-distributions_by_types} demonstrates how the distribution of weights change with the community type used to induce the partition. For example, the second column shows how the distributions of hashtag weights change based on the community partition. Unsurprisingly, we see that the greatest difference between the distributions occurs when we consider the topic-based communities, since the topic-based communities are determined based on the hashtag weights. However, we also see differences in the distributions when the Community-type / Weight-type pairs do not match. For example, for the covering corresponding to the activity-based communities, the hashtag weights tend to be higher for edges internal to communities than between communities. Similarly, for the covering corresponding to the topic-based communities, the transfer entropy weights tend to be higher on edges within (intra) and between (inter) communities, and lower for edges between members with multiple, non-identical memberships (multi).

@@

>>>>

Each community type (Structural, Activity-based, Topic-based, Interaction-based) induces a different partition of the edges, and each edge type (Transfer Entropy, Hashtag, Mention-Retweet) induces a different distribution of weights. That is, let $W_{u \to f}$ be the weight on a randomly selected edge $E_{u \to f}$ from the network, and compute
\begin{align}
	P(W_{u \to f} \leq w | T(E_{u \to f}) = t),
\end{align}
the empirical distribution over the edge weights conditioned on $t$ being one of inter, intra, and multi. For meaningful community structure, we expect the distribution of edge weights to differ with the edge type $t$. If the community structure were arbitrary, the edge weights would be independent of the edge type, and all three conditional distributions would be identical.
These distributions are shown in Figure~\ref{Fig-distributions_by_types}.

Each \emph{column} of Figure~\ref{Fig-distributions_by_types} demonstrates how the distribution of weights change with the community type used to induce the partition. For example, the second column shows how the distributions of hashtag weights change based on the community partition. In general, the distributions differ in non-trivial ways across the edge types and coverings. However, we see that the medians of the distributions provide a useful summary statistic. Under each collection of distribution functions, we list the median value of the inter, intra, and multi-edges in red, blue, and magenta, respectively. Unsurprisingly, we see that the greatest difference between the distributions occurs when we consider the topic-based communities, since the topic-based communities are determined based on the hashtag weights. However, we also see differences in the distributions when the Community-type / Weight-type pairs do not match. For example, for the covering corresponding to the activity-based communities, the hashtag weights tend to be higher for edges internal to communities than between communities. Similarly, for the covering corresponding to the topic-based communities, the transfer entropy weights tend to be higher on edges within (intra) and between (inter) communities, and lower for edges between members with multiple, non-identical memberships (multi).

@@

We also note that the distribution of transfer entropy weights always tend to be higher for edges crossing community boundaries (inter- or multi-edges) compared to those edges within community boundaries (intra-edges). This is a property not exhibited by either the hashtag or mention-retweet weights, independent of the covering used to partition the edges. Moreover, for all but the activity-based covering, the weights of multi-edges tend to be highest overall.  Recall that the transfer entropy $\text{TE}_{X(u) \to X(f)}$ quantifies the reduction in uncertainty about a follower $f$'s activity from knowing the activity of a user $u$. This result therefore implies that, in terms of prediction, it is more useful to know the time series of a user followed outside of the community compared to a user followed inside of the community, and even more useful to know the time series of a user that shares some, but not all, of the same community memberships. Thus, in an information theoretic sense, we see that novel information useful for prediction is more likely to flow \emph{across} community boundaries than \emph{within} community boundaries.
